Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-03-23 SIR_manuscript.tex
fixed van den in bib

\todo{the algebra needs to be changed based on JD's comment} The Disease-Free Equilibrium (DFE) for the SIR model, Eqs. \eqref{model}, is given by setting the differential equations to 0 and solving for the unknowns (\ali{is this clear or the "unkowns" needs to be defined? also * in sup for I and R?}. The DFE is
\begin{equation}
\label{dfe}
S\_n^*= \frac{\rho}{\omega} N_0, \ S\_u^*= N_0-S\_n^*, \text{~and~} I_j=R_j=0 \ \text{for all }j.
\end{equation}

The basic reproduction number, $\Rnum$, was calculated by using the next generation matrix method developed by \cite{van2002reproduction}. $\Rnum$ is
\begin{equation}
\label{R0}
\Rnum= \frac{\beta}{\gamma} (1-\Delta), 
\end{equation}
where
\begin{equation}
\begin{aligned}
\label{eq:abc}
\Delta=& 1-(A~ S\_u^* + B~ S\_n^*)~ C\\
A=& \gamma(\omega+\gamma) + (\gamma \eta\_w + \omega \eta\_c p_I) F_I, \\
B=& \big(\omega+(F_I+\gamma)\eta\_w\big) \gamma+\frac{(\eta\_w \gamma+ \eta\_c\omega) \omega p_I F_I }{\omega+\gamma}, \\ 
C=& \frac{1}{N_0 (\gamma(\omega+\gamma)+F_I(\gamma+\omega p_I))}.
\end{aligned}
\end{equation}
Further details of derivation of $\Rnum$ are provided in the appendix section.

>>>>

\todo{the algebra needs to be changed based on JD's comment} The Disease-Free Equilibrium (DFE) for the SIR model, Eqs. \eqref{model}, is given by setting the differential equations to 0 and solving for the unknowns (\ali{is this clear or the "unkowns" needs to be defined? also * in sup for I and R?}. The DFE is
\begin{equation}
\label{dfe}
S\_n^*= \frac{\rho}{\omega} N_0, \ S\_u^*= N_0-S\_n^*, \text{~and~} I_j=R_j=0 \ \text{for all }j.
\end{equation}
For simplification of the analysis, we adopt the following change $x\_u^* = S\_u^*/N_0$ and $x\_n^* = S\_n^*/N_0$.

The basic reproduction number, $\Rnum$, was calculated by using the next generation matrix method developed by \cite{van2002reproduction}. $\Rnum$ is
\begin{equation}
\label{R0}
\Rnum= \frac{\beta}{\gamma} (1-\Delta), 
\end{equation}
where
\begin{equation}
\begin{aligned}
\label{eq:abc}
\Delta=& (A~ \theta\_w + B~ \theta\_c)~ C\\
A=& \gamma \big((\omega+\gamma)+\omega p_I F_I \big) \big(x_n^*+\gamma(\omega+\gamma)F_I \big)\\
B=& \omega p_I F_I (\gamma x_u^*+\omega) \\ 
C=& \frac{1}{(\omega+\gamma) \big(\gamma(\omega+\gamma)+F_I(\gamma+\omega p_I) \big)}.
\end{aligned}
\end{equation}
% \begin{equation}
% \label{R0}
% \Rnum= \frac{\beta}{\gamma} (1-\Delta), 
% \end{equation}
% where
% \begin{equation}
% \begin{aligned}
% \label{eq:abc}
% \Delta=& 1-(A~ S\_u^* + B~ S\_n^*)~ C\\
% A=& \gamma(\omega+\gamma) + (\gamma \eta\_w + \omega \eta\_c p_I) F_I, \\
% B=& \big(\omega+(F_I+\gamma)\eta\_w\big) \gamma+\frac{(\eta\_w \gamma+ \eta\_c\omega) \omega p_I F_I }{\omega+\gamma}, \\ 
% C=& \frac{1}{N_0 (\gamma(\omega+\gamma)+F_I(\gamma+\omega p_I))}.
% \end{aligned}
% \end{equation}
Further details of derivation of $\Rnum$ are provided in the appendix section.
